Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
update section VIII and ASR figs with correct MFCCs frequency range

For both MFCCs and scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{early}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{early}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes.

Lastly, we see that while \emph{ob-c} and \emph{ob-w} perform equivalently for the MFCCs, \emph{ob-c} seems to be able to better characterize the classes than \emph{ob-w} for scattering coefficients. This last observation suggests that weighted a centroid according to the number of frames belonging to it may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources.

>>>>

For the scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{early}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{early}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes. Furthermore It appears that \emph{ob-c} is be able to better characterize the classes than \emph{ob-w}. This last observation suggests that weighted a centroid according to the number of frames belonging to it may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources.

For the MFCCs, there is no clear evidence that the \emph{ob} approaches improve the results.
